### 2020-07-06 paper.Rmd
minor stuff paper

In my treatment of k-means clustering, I adopt the notation Steinley 
(2006) provided in his thorough synthesis of the k-means literature. In 
clustering---or anticlustering---, an item pool $X$ = $\{x_1, \ldots, 
x_N\}$ has to be partitioned into $K$ groups $\{C_1, \ldots, C_K\}$. We 
will refer to the groups $C_j$, $j = 1, \ldots, K$, as anticlusters, 
clusters, or groups, and to the collection of anticlusters $C$ as the 
partitioning of the data set. We assume that each element $x_i$ ($i = 1, 
\ldots, N$), is a vector of length $P$, and each entry describes one of 
its numeric measurements. Generally hence, $X$ can be interpreted as an 
$N \times M$ matrix where each row represents an data point $x_i$ (e.g., 
representing a stimulus or a person) and each column is a numeric 
attribute (e.g., the number of syllables in a word, or the 
attractiveness rating of a face).

K-Means anticlustering aims to maximize the error sum of squares (SSE), 
also known as the within-group variance, which is the sum of the 
squared Euclidean distances between each data point and its cluster 
centroid. The cluster centroid is given by averaging the values on each 
variable over the elements within that cluster. The centroid of the 
*j*th variable in the *k*th cluster, consisting of $n_k$ elements, is 
given as:

@@

@@

>>>>

In this treatment of k-means, I adopt the notation Steinley (2006) 
provided in his synthesis of the k-means literature. In clustering---or 
anticlustering---, an item pool $X$ = $\{x_1, \ldots, x_N\}$ has to be 
partitioned into $K$ groups $\{C_1, \ldots, C_K\}$. We assume that each 
element $x_i$ ($i = 1, \ldots, N$), is a vector of length $P$, and each 
entry describes one of its numeric measurements. Generally, $X$ 
can is interpreted as an $N \times M$ matrix where each row represents 
an data point $x_i$ (e.g., representing a stimulus or a person) and each 
column is a numeric attribute (e.g., the number of syllables in a word, 
or the attractiveness rating of a face).

K-Means anticlustering aims to maximize the error sum of squares (SSE), 
the within-group variance, which is the sum of the squared Euclidean 
distances between each data point and its cluster centroid. The cluster 
centroid is given by averaging the values on each variable over the 
elements within that cluster. The centroid of the *j*th variable in the 
*k*th cluster, consisting of $n_k$ elements, is given as:

@@

In anticlustering applications, we usually assume that all cluster are 
of equal size. Hence

$$
n_k = \frac{N}{K}, \forall k \in \{1, \ldots, K\}
$$

@@

- Two examples: $K = 2$, $N = 20$ vs. $N = 100$, using classical
k-means: only mean; using k-variance: only variance; combination:
both, but works better for larger $N$

# Weighted k-means

Using variable weighting (see Steinley, 2006, p. 13), we can 
adjust the relative importance of minimizing differences in means
and variances. Standard in `anticlust`: Equal weight, this is 
achieved by first creating the new variables, representing 
the squared differences from the mean, and then standardizing
the entire feature matrix. If $N$ is large enough (relative to $K$),
there is usually no need for weighting.

# Simulation

- show that k-variance anticlustering outperforms other objectives

# Examples

- use some examples (e.g., OASIS data set)
